
\section{Requirements Specification}\label{section:requirements}
Due to the scope of the project it would be impossible to commence without a clear vision of how
the end product should function. These requirements were decided on during the early stages of the project. 
The reasoning behind them comes primarily from a number of sources:
\begin{itemize}
 \item Research into a previous attempt at old SICSA system.
 \item Research into what makes a search result a good result.
 \item Research into learning to rank techniques to enhancing the performance of the retrieval system by integrating different kinds of expertise evidence.
 \item Discussion with Dr. Craig Macdonald.
\end{itemize}
However, developing an IR system is researched based. Utilizing learning to rank technique might not 
produce optimal ranking due to the lack of training dataset. Therefore, The requirements have been split into several sections depending on their 
necessity.

\subsubsection{Must Have}
\begin{itemize}
 \item Extracting funded projects from different 2 sources: Grant on the Web~\cite{gow} and Research Councils UK~\cite{gtr}.
 \item Integrating publications and funded projects as expertise evidence.
 \item Mining expertise evidence.
 \item Utilizing learning to rank techniques with an attempt to enhance the performance of the retrieval system.
 \item Indexing and Retrieving documents (experts) effectively.
 \item Able to conclude that applying learning to rank techniques helps improve the performance of the retrieval system. 
\end{itemize}

I will discuss with u about this section tomorrow

